Viscous Transport in Eroding Porous Media

### 2019-06-14 docs/transport/erosion_transport.tex
do the result in transport paper

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/velocity_loc20_268}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_local20_268}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/diff_tort20_268}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/uminDumax20_268}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20tort} The tortuosity of the 20 nearly touching bodies 
when the porosity is 62.9 \% and the tortuosity is 1.0979.
(a) The 
x-component velocity u(-1, y) with respect to its maximum velocity $u_{max}=2.9828
\times 10^{-3}$ at equal spreading tracers on the cross section x = -1. 
(b) The local tortuosity $\tau(y)$ on the cross section x = -1. 
(c) The difference of $\tau(y)$ at two neighboring tracers on the cross section x = -1.
(d) The ratio of the minimum to maximum speeds along the trajectories of tracers.}
\end{figure}

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/tort_diff_top10_268}
\caption{\label{fig:Eroding20tort_traj} The largest 10 difference of 
local tortuosity $\tau$ at two neighboring tracers in
 20 nearly touching bodies eroding. The same color of a pair of trajectories 
means they are from two neighboring tracers.}
\end{figure}

@@

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/velocity_loc100}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_local100}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/diff_tort100}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/uminDumax100}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding100tort} The tortuosity of the 100 bodies when the porosity is 62.98 \%
and the tortuosity is 1.1182.}
\end{figure}

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/tort100b_diff_top50}
\caption{\label{fig:Eroding100tort_traj} The largest 50 difference of 
local tortuosity $\tau$ at two neighboring tracers in
100 bodies eroding. The same color of a pair of trajectories 
means they are from two neighboring tracers.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{s:conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/velocity_loc20_268}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_local20_268}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/diff_tort20_268}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/uminDumax20_268}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20tort} The tortuosity study in the fluid with 20 nearly touching bodies.
(a) The 
x-component velocity u(-1, y) with respect to its maximum velocity $u_{max}=2.9828
\times 10^{-3}$ at equal spreading tracers on the cross section x = -1. 
(b) The local tortuosity $\tau(y)$ on the cross section x = -1. 
(c) The difference of $\tau(y)$ at two neighboring tracers on the cross section x = -1.
(d) The ratio of the minimum to maximum speeds along the trajectories of tracers.}
\end{figure}

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/tort_diff_top10_268}
\caption{\label{fig:Eroding20tort_traj} The largest 10 difference of 
local tortuosity $\tau$ at two neighboring tracers in
 20 nearly touching bodies eroding when the porosity is 62.9 \% 
and the tortuosity is 1.0979. The same color of a pair of trajectories 
means they are from two neighboring tracers.}
\end{figure}

@@

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/velocity_loc100}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_local100}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/diff_tort100}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/uminDumax100}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding100tort} The tortuosity study in the fluid with 100 bodies. }
\end{figure}

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/tort100b_diff_top50}
\caption{\label{fig:Eroding100tort_traj} The largest 50 difference of 
local tortuosity $\tau$ at two neighboring tracers in
100 bodies eroding when the porosity is 62.98 \%
and the tortuosity is 1.1182. The same color of a pair of trajectories 
means they are from two neighboring tracers.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{s:conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
